Algomusicology, ????, Profit

### 2016-06-12 paper.tex
Remove prefixed import for consistency.
Add publishers to references.

\begin{verbatim}
(fact
  (->> (leipzig/phrase [2/3 1/3] [0 4]) encode)
    => 23001304)
\end{verbatim}

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel, \textit{The Garden of Forking Paths}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, 1933.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Ser}, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, 1985.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{CACM}, 2015.
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.

>>>>

\begin{verbatim}
(fact
  (->> (phrase [2/3 1/3] [0 4]) encode)
    => 23001304)
\end{verbatim}

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, 1933.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Ser}, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, 2015.
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.
